---
title: "Hywind Scotland - Data analyses"
author: "[Pierre Priou](ppr@akvaplan.niva.no)"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: show
    toc: true
    toc_float: true
    toc_collapsed: true
---

This document contains the code for analyzing EK80 data from the Hywind Scotlan survey.

# Packages required

```{r load-packages, message=FALSE}
library(tidyverse)  # Tidy code
library(sf)         # Spatial data
library(lemon)      # Nice facets
```

Set figure theme.

```{r update-fig-theme}
# Theme for figures
theme_set(theme_bw())
theme_update(panel.grid = element_blank(), 
             panel.border = element_blank(), 
             axis.line = element_line(),
             axis.text = element_text(size = 8),
             axis.title = element_text(size = 9),
             legend.title = element_text(size = 9),
             strip.text.x = element_text(size = 8, face = "plain", hjust = 0.5),
             strip.background = element_rect(colour = "transparent",  fill = "transparent"),
             legend.margin = margin(0, 0, 0, 0),
             legend.box.margin = margin(0, 0, -8, 0),
             plot.margin = unit(c(0.05, 0.05, 0.05, 0.05), "in"))
```
# Data loading

Virginie provided a `.Rdata` file that contained all the data.

```{r load-data}
load("data/analyses Gin/2023_Reanalysis.RData")
```

Tidy dataframes.

```{r tidy-data}
Sv_tidy <- Integration_10mDB_sfp %>% 
  # Rename variables
  rename(depth = Layer_depth_min) %>% 
  # Unite date and time
  unite(date_S, Date_S, Time_S, sep = " ", remove = F) %>%
  # Fix variable type and tidy
  mutate(date = date(SampleTime),
         date_S = ymd_hms(date_S, tz = "UTC"),
         period = cut(date, breaks = seq(min(date) - 1, max(date), 6), right = T, include.lowest = T),
         time_floor = hms::as_hms(floor_date(date_S, "20 mins")), 
         hour = hour(date_S),
         sv_lin = 10 ^ (Sv_mean / 10),
         DistCat = factor(DistCat),
         area = factor(if_else(DistCat == "Outside", "outside", "inside"))) %>%
  # Tidy data set
  filter(Sv_mean < 0 & is.na(NASC) == F & Height_mean >= 9) %>% 
  # Select only relevant variables
  select(date_S, time_floor, hour, period, area, depth, sv_lin, NASC) %>% 
  st_drop_geometry()
```

# Analyses
 
## Synthetic echograms

Calculate mean Sv and NASC per 10 m cell per hour inside and outside the park per period (~ 1 week).

```{r 24h-summary}
MVBS_24h <- Sv_tidy %>% 
  group_by(area, period, hour, depth) %>% 
  summarise(sv_lin = mean(sv_lin, na.rm = T),
            NASC_mean = mean(NASC, na.rm = T),
            n = n()) %>% 
  ungroup() %>% 
  mutate(Sv_mean = 10 * log10(sv_lin))
```

Create a synthetic echogram for inside / outisde the park per week.

```{r synthetic-echograms}
MVBS_24h %>% 
  ggplot() +
  geom_raster(aes(x = hour, y = depth, fill = Sv_mean)) + 
  scale_fill_viridis_c(option = "turbo") + 
  scale_y_reverse() + 
  facet_rep_grid(period ~ area, repeat.tick.labels = T)
```

Count of samples used to calculate mean Sv.

```{r count-echograms}
MVBS_24h %>% 
  ggplot() +
  geom_raster(aes(x = hour, y = depth, fill = n)) + 
  scale_fill_viridis_c(option = "viridis") +
  scale_y_reverse() + 
  facet_rep_grid(period ~ area, repeat.tick.labels = T)
```

